---
title: "Hannah Fleming - elastic net"
author: "Laura Pyle"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
library(knitr)
library(skimr)
library(arsenal)
library(doParallel)
library(naniar)
library(ensr)
library(tidyverse)
library(broom)

knitr::opts_chunk$set(echo = FALSE,warning = FALSE)

source("~/Documents/Github/shared-resources/Machine Learning/Tim - ElasticNet CV/easy_elasticnet.R")
```

```{r data, include=FALSE}
data <- read.csv("~/pylell/Fleming dissertation/Data_raw/exportaim1_2matchCATEGORIES.csv", na.strings = c(".",""," "))
data$Maternal_Race <- as.factor(data$Maternal_Race)
data$GT_at_discharge <- as.factor(data$GT_at_discharge)
data$gender <- as.factor(data$gender)
data$Mother_of_Hispanic_Origin <- as.factor(data$Mother_of_Hispanic_Origin)
data$primary_language <- as.factor(data$primary_language)
data$complication_of_pregnancy_IDM__D <- as.factor(data$complication_of_pregnancy_IDM__D)
data$prenatal_drug_exposure <- as.factor(data$prenatal_drug_exposure)
data$type_of_respiratory_support_at_d <- as.factor(data$type_of_respiratory_support_at_d)
data$SGA_AGA_LGA <- as.factor(data$SGA_AGA_LGA)
data$diagnosis_of_GERD_by_end_of_NICU <- as.factor(data$diagnosis_of_GERD_by_end_of_NICU)
data$Neuro_injury_on_head_ultrasound <- as.factor(data$Neuro_injury_on_head_ultrasound)
data$diagnosis_of_dysphagia_per_instr <- as.factor(data$diagnosis_of_dysphagia_per_instr)
data$diagnosis_of_oral_aversion <- as.factor(data$diagnosis_of_oral_aversion)
data$diagnosis_of_NEC_YN <- as.factor(data$diagnosis_of_NEC_YN)
data$feeds_initiated_on_LFNC_vs_HFNC <- as.factor(data$feeds_initiated_on_LFNC_vs_HFNC)
data$diagnosis_of_BPD <- as.factor(data$diagnosis_of_BPD)
data$Season_of_Discharge <- as.factor(data$Season_of_Discharge)
data$diagnosis_of_failure_to_thrive_i <- as.factor(data$diagnosis_of_failure_to_thrive_i)
data$Rural <- as.factor(data$Rural)
data$COVID <- as.factor(data$COVID)
data$gestage_cat <- as.factor(data$gestage_cat)
data$payor_cat <- as.factor(data$payor_cat)
data$ventduration_cat <- as.factor(data$ventduration_cat)
data$SiPAP_NIMV_cat <- as.factor(data$SiPAP_NIMV_cat)
data$NCPAP_cat <- as.factor(data$NCPAP_cat)
data$HFNC2L_cat <- as.factor(data$HFNC2L_cat)
data$NC2_cat <- as.factor(data$NC2_cat)
data$IVH_cat <- as.factor(data$IVH_cat)

# make df with highest priority variables
data_high <- data[,c("GT_at_discharge","Maternal_Race","BW","gender","Mother_of_Hispanic_Origin","primary_language","complication_of_pregnancy_IDM__D",
                     "prenatal_drug_exposure","X_1_minute","X_5_minute","X_10_minute","type_of_respiratory_support_at_d","SGA_AGA_LGA","diagnosis_of_GERD_by_end_of_NICU",
                     "Neuro_injury_on_head_ultrasound","diagnosis_of_dysphagia_per_instr","diagnosis_of_oral_aversion","diagnosis_of_NEC_YN","feeds_initiated_on_LFNC_vs_HFNC",
                     "diagnosis_of_BPD","Season_of_Discharge","caloric_density_of_prescribed_fo","Caloric_density_of_Human_Milk_if","diagnosis_of_failure_to_thrive_i",
                     "Rural","COVID","gestage_cat","payor_cat","ventduration_cat","SiPAP_NIMV_cat","NCPAP_cat","HFNC2L_cat","NC2_cat","IVH_cat")]
data_high <- data_high[complete.cases(data_high),]
```

# Descriptive Statistics

```{r include=TRUE, warning=FALSE, message=F}
t1 <- tableby(data=data_high, GT_at_discharge ~  Maternal_Race + BW + gender + Mother_of_Hispanic_Origin + primary_language + complication_of_pregnancy_IDM__D + prenatal_drug_exposure + 
                X_1_minute +  X_5_minute + X_10_minute  + type_of_respiratory_support_at_d + SGA_AGA_LGA + diagnosis_of_GERD_by_end_of_NICU + Neuro_injury_on_head_ultrasound + 
                diagnosis_of_dysphagia_per_instr + diagnosis_of_oral_aversion + diagnosis_of_NEC_YN + feeds_initiated_on_LFNC_vs_HFNC + diagnosis_of_BPD + Season_of_Discharge + 
                caloric_density_of_prescribed_fo + Caloric_density_of_Human_Milk_if + diagnosis_of_failure_to_thrive_i + Rural + COVID + gestage_cat + payor_cat + ventduration_cat + 
                SiPAP_NIMV_cat + NCPAP_cat + HFNC2L_cat + NC2_cat + IVH_cat, numeric.stats=c("Nmiss2","median","q1q3"))
kable(summary(t1))
```

# Run elastic net and refit the final model using all high priority variables  (note: estimates have been exponeniated to ORs)

```{r include=TRUE, warning=FALSE, message=F}
mod = easy_elasticnet(data = data_high,outcome = "GT_at_discharge",
                           predictors = c("Maternal_Race","BW","gender","Mother_of_Hispanic_Origin","primary_language","complication_of_pregnancy_IDM__D",
                     "prenatal_drug_exposure","X_1_minute","X_5_minute","X_10_minute","type_of_respiratory_support_at_d","SGA_AGA_LGA","diagnosis_of_GERD_by_end_of_NICU",
                     "Neuro_injury_on_head_ultrasound","diagnosis_of_dysphagia_per_instr","diagnosis_of_oral_aversion","diagnosis_of_NEC_YN","feeds_initiated_on_LFNC_vs_HFNC",
                     "diagnosis_of_BPD","Season_of_Discharge","caloric_density_of_prescribed_fo","Caloric_density_of_Human_Milk_if","diagnosis_of_failure_to_thrive_i",
                     "Rural","COVID","gestage_cat","payor_cat","ventduration_cat","SiPAP_NIMV_cat","NCPAP_cat","HFNC2L_cat","NC2_cat","IVH_cat"),
                           model_type = "binomial")

# refit the model
f_mod = as.formula(paste0("GT_at_discharge~",paste0(mod,collapse = "+")))
refit_mod = glm(formula = f_mod,data = data_high,family = "binomial")
kable(tidy(refit_mod, exponentiate=T),digits = 3)

```

# Reduced elastic net and refit the final model (note: estimates have been exponeniated to ORs)

Variables entered into the elastic net include birthweight, gender, mother of Hispanic origin, Apgar scores at 1, 5, and 10 minutes.

```{r include=TRUE, warning=FALSE, message=F}
mod = easy_elasticnet(data = data_high,outcome = "GT_at_discharge",
                           predictors = c("BW","gender","Mother_of_Hispanic_Origin","X_1_minute","X_5_minute","X_10_minute"),
                           model_type = "binomial")

# refit the model
f_mod = as.formula(paste0("GT_at_discharge~",paste0(mod,collapse = "+")))
refit_mod = glm(formula = f_mod,data = data_high,family = "binomial")
kable(tidy(refit_mod, exponentiate=T),digits = 3)

```