---
title: "INFLUENTIAL - PAS abstract"
author: "Laura Pyle"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r libraries,echo=FALSE, include=F}
library(segmented)
library(knitr)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(arsenal)
library(stringr)

knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE)
```

```{r,echo=FALSE, include=F}
check_vaccination_dates_new <- function(data) {
  # Create new columns for the results, default to 0
  data$vaccine_this_season <- 0
  data$vaccine_during_hosp <- 0
  
  # Get column names for vaccination dates
  vaxx_cols <- paste0("fluvaxxdate_", 1:29)
  
  # Loop through each row in the dataset
  for (i in 1:nrow(data)) {
    # Get the screening date range for this person
    #first_date <- data$first_screen[i]
    #last_date <- data$last_screen[i]
    season <- data$season[i]
    start_year <- substr(season, 1, 4)
    end_year <- substr(season, 6, 10)
    first_date <- make_date(year = start_year, month = 8, day = 1)
    last_date <- make_date(year = end_year, month = 6, day = 30)
    adm_date <- data$adm_date[i]
    dish_date <- data$dish_date[i]
    
    # Skip if screening dates or admission date are missing
    if (is.na(first_date) || is.na(last_date) || is.na(adm_date) || is.na(dish_date)) {
      next
    }
    
    # Check each vaccination date column
    for (col in vaxx_cols) {
      # Skip if this vaccination date is missing
      if (is.na(data[[col]][i]) || data[[col]][i] == "") {
        next
      }
      
      vaxx_date <- data[[col]][i]
      
      # Check if vaccination date is within screening period
      if (vaxx_date >= first_date && vaxx_date <= last_date) {
        
        # Condition 1: Vaccination before hospital admission
        if (vaxx_date < adm_date) {
          data$vaccine_this_season[i] <- 1
        }
        
        # Condition 2: Vaccination during hospitalization
        if (!is.na(dish_date) && 
            vaxx_date >= adm_date && 
            vaxx_date <= dish_date) {
          data$vaccine_during_hosp[i] <- 1
        }
      }
    }
  }
  
  return(data)
}
```

```{r data,echo=FALSE,warning=FALSE}
# latest dataset should contain EPIC and Cerner data
redcap <- read.csv('/Users/pylell/Library/CloudStorage/OneDrive-SharedLibraries-UW/Rao/ID Week abstract/Data raw/InFLUentialMainSites_DATA_2025-04-20_1846.csv')

# remove records with missing site number
alldata <- redcap %>% filter(!is.na(site))
alldata$site_long <- ifelse(alldata$site == "M1", "SCH",
                            ifelse(alldata$site == "M2", "CHCO", "Lurie"))

# combine contraindication columns
alldata <- alldata %>% mutate(
  contraindication_summary = pmax(alldata$contraindication, alldata$contraindication2, na.rm = T)
)
# combine previous vaccination columns
alldata$screen_priorvacc1 <- ifelse(alldata$screen_priorvacc1 == 98, NA, alldata$screen_priorvacc1)
alldata$screen_priorvacc2 <- ifelse(alldata$screen_priorvacc2 == 98, NA, alldata$screen_priorvacc2)
alldata <- alldata %>% mutate(
  priorvacc_summary = pmax(alldata$screen_priorvacc1, alldata$screen_priorvacc2, na.rm = T)
)

# first thing to do is to limit the hospitalizations to those between first and last screening date per season
alldata$screen_date1 <- ifelse(alldata$screen_date1 %in% c("", " "), NA, alldata$screen_date1)
alldata$screen_date2 <- ifelse(alldata$screen_date2 %in% c("", " "), NA, alldata$screen_date2)
# find first and last screen date by site
s1 <- alldata %>% dplyr::select(site, screen_date1)
colnames(s1) <- c("site", "Screen Date")
s2 <- alldata %>% dplyr::select(site, screen_date2)
colnames(s2) <- c("site", "Screen Date")
s <- rbind(s1, s2)
s$`Screen Date` <- as.Date(s$`Screen Date`, format = "%Y-%m-%d")
s <- s %>% filter(!is.na(`Screen Date`))
s_unique <- unique(s)
# write screening dates to file
#write.csv(s_unique, "/Volumes/pylell/Rao/PHM abstract/screen_dates.csv", row.names = FALSE)

# summarize screening data by site
# first create a variable for season using August 1 as earliest date and June 1 as latest
# using screening data not admissions data because we want to know when sites stopped and started screening
site_data <- alldata
site_data <- site_data %>%
  mutate(
    season = case_when(
      screen_date1>"2018-08-01" & screen_date1<"2019-06-01" ~ "2018-2019",
      screen_date1>"2019-08-01" & screen_date1<"2020-06-01" ~ "2019-2020",
      screen_date1>"2020-08-01" & screen_date1<"2021-06-01" ~ "2020-2021",
      screen_date1>"2021-08-01" & screen_date1<"2022-06-01" ~ "2021-2022",
      screen_date1>"2022-08-01" & screen_date1<"2023-06-01" ~ "2022-2023",
      screen_date1>"2023-08-01" & screen_date1<"2024-06-01" ~ "2023-2024",
      .default = NA
    )
  )
# for purposes of finding earliest and latest screen dates by site and season,
# remove hospitalizations with no screening or outside possible date range
site_data <- site_data %>% filter(!is.na(season))
screen_dates <- site_data %>% group_by(site_long, season) %>% summarise(first_screen = min(screen_date1),
                                                                   last_screen = max(screen_date1))

# in the patient level data, create a variable for season based on admission date
# merge in the site level data by site and season and exclude hospitalizations
# outside the date range for that season
# make sure both admission and discharge are within the first and last dates of screening
alldata <- alldata %>%
  mutate(
    season = case_when(
      adm_date>"2018-08-01" & adm_date<"2019-06-01" ~ "2018-2019",
      adm_date>"2019-08-01" & adm_date<"2020-06-01" ~ "2019-2020",
      adm_date>"2020-08-01" & adm_date<"2021-06-01" ~ "2020-2021",
      adm_date>"2021-08-01" & adm_date<"2022-06-01" ~ "2021-2022",
      adm_date>"2022-08-01" & adm_date<"2023-06-01" ~ "2022-2023",
      adm_date>"2023-08-01" & adm_date<"2024-06-01" ~ "2023-2024",
      .default = NA
    )
  )
alldata <- left_join(alldata, screen_dates, by = c("site_long", "season"))
alldata$in_window <- ifelse(as.Date(alldata$adm_date)>=alldata$first_screen &
                                   as.Date(alldata$dish_date)<=alldata$last_screen, "Y", "N")
alldata$season_num <- ifelse(alldata$season == "2018-2019", 1, 
                             ifelse(alldata$season == "2019-2020", 2,
                                    ifelse(alldata$season == "2020-2021", 3, 
                                    ifelse(alldata$season == "2021-2022", 4, 
                                           ifelse(alldata$season == "2022-2023", 5, 
                                                  ifelse(alldata$season == "2023-2024", 6, NA))))))
# no screening data for Lurie in 2018-2019, so will exclude all admissions there for the season
x <- alldata[is.na(alldata$in_window) | alldata$in_window == "N",]
num_excluded <- nrow(x)

# add month of year admitted
alldata$month_adm <- month(alldata$adm_date)

# create new variable for English/Spanish/Other
alldata$eng_span_other <- ifelse(alldata$language == 17, "English",
                                 ifelse(alldata$language == 43, "Spanish", "Other"))

######################
# INCLUSION CRITERIA #
######################

# between 6 months and 18 years at time of discharge
alldata$dish_date <- as.Date(alldata$dish_date)
alldata$adm_date <- as.Date(alldata$adm_date)
alldata$los <- as.numeric(alldata$dish_date - alldata$adm_date)
# all records above seem to have Discharge after Admission 
# no negative LOS, but some 0 LOS
alldata$age_discharge_days <- alldata$age_admission + alldata$los
alldata$age_discharge_yrs <- (alldata$age_admission + alldata$los)/365.25
alldata$age_discharge_mo <- (alldata$age_admission + alldata$los)/30.437
# age at admission
alldata$age_admission_yrs <- alldata$age_admission/365.25
alldata$age_admission_mo <- alldata$age_admission/30.437

######################
# EXCLUSION CRITERIA #
######################

# apply eligibility criteria
data <- alldata
data$eligible_age <- as.factor(ifelse(data$age_admission_mo >= 6 & data$age_admission_yrs <= 18, 1, 0))
# Patient hospitalized on a medical, surgical, rehabilitation, or psychiatry/behavioral medicine unit during the influenza vaccination season at your institution
data$eligible_season <- as.factor(ifelse(!is.na(alldata$in_window) & alldata$in_window == "Y", 1, 0))
data$eligible_unit <- as.factor(ifelse(data$unit %in% c(32,99), 0, 1))
# Admitted to hematology/oncology service or unit
data$eligible_service <- as.factor(ifelse(is.na(data$service) | data$service == 32, 0, 1))
data_all <- data
data_all$eligible <- ifelse(data_all$eligible_age == 1 & data_all$eligible_season ==1 &
                              data_all$eligible_service == 1 & data_all$eligible_unit ==1, 1, 0)
# Discharged from ICU setting
#data$eligible_icu <- as.factor(ifelse(data$icu == 1, 0, 1))
# Ward of state or foster child
# NO CORRESPONDING VARIABLE
# Death on record
# NO CORRESPONDING VARIABLE
# Flagged as “Does not wish to participate in research” 
# NO CORRESPONDING VARIABLE

# print those ineligible due to unit and service
write.csv(data[data$eligible_unit == 0,], '/Users/pylell/Library/CloudStorage/OneDrive-SharedLibraries-UW/Rao/PHM abstract/ineligible_unit.csv')
write.csv(data[data$eligible_service == 0,], '/Users/pylell/Library/CloudStorage/OneDrive-SharedLibraries-UW/Rao/PHM abstract/inelgible_service.csv')

# remove ineligible patients
eligible <- data %>% filter(eligible_age == 1)
eligible <- eligible %>% filter(eligible_season == 1)
eligible <- eligible %>% filter(eligible_unit == 1)
eligible <- eligible %>% filter(eligible_service == 1)
#eligible <- eligible %>% filter(eligible_icu == 1)

# figure out how many eligible patients 
eligible_ptct <- eligible
eligible_ptct$pid <- substr(eligible_ptct$hid, 1, 8)
#length(unique(eligible_ptct$pid))

# count of unique eligible patients by site and season
eligible_unique <- eligible %>% dplyr::select(site_long, season, sid) %>% unique()
#eligible_summary <- eligible %>% group_by(site_long, season) %>% summarise(patient_count = tally())

# count of unique hospitalizations for eligible patients by site and season
eligible_hosp_unique <- eligible %>% dplyr::select(site_long, season, hid) 
#eligible_hosp_summary <- eligible_hosp_unique %>% group_by(site_long, season) %>% summarise(hospitalization_count = tally())

# find hospitalizations who were screened
eligible_screened <- eligible 
eligible_screened_save <- eligible_screened
eligible_screened_save$contraindication_summary_bin <- ifelse(is.na(eligible_screened_save$contraindication_summary) |
                                                                eligible_screened_save$contraindication_summary == 0, 0, 1)
eligible_screened <- eligible_screened %>% filter(screening == 1)
es <- as.data.frame(table(eligible_screened$site_long, eligible_screened$season))
colnames(es) <- c("site_long", "season", "# Screenings")

# create a table with number of hospitalizations and screenings
t2 <- as.data.frame(table(eligible_hosp_unique$site_long, eligible_hosp_unique$season))
colnames(t2) <- c("site_long", "season", "hospitalizations")
t2 <- left_join(t2, es, by = c("site_long", "season"))
t2$percent_screened <- round((t2$`# Screenings` / t2$hospitalizations) * 100,2)

# find those screened with contraindications
eligible_screened_contra <- eligible_screened %>% filter(contraindication_summary == 1)
cs <- as.data.frame(table(eligible_screened_contra$site_long, eligible_screened_contra$season))
colnames(cs) <- c("site_long", "season", "# w/ contraindications")
t3 <- as.data.frame(table(eligible_hosp_unique$site_long, eligible_hosp_unique$season))
colnames(t3) <- c("site_long", "season", "hospitalizations")
t3 <- left_join(t3, cs, by = c("site_long", "season"))
t3 <- left_join(t3, es, by = c("site_long", "season"))
t3$`# w/ contraindications` <- ifelse(is.na(t3$`# w/ contraindications`), 0, t3$`# w/ contraindications`)
t3$percent_contraindication <- round((t3$`# w/ contraindications` / t3$`# Screenings`) * 100,2)

# Find hospitalizations without contraindications and no vaccination this season (i.e., eligible for vaccine)
eligible_screened_no_contra <- eligible_screened %>% 
  filter(contraindication_summary == 0 | is.na(contraindication_summary))
# determine whether patient had a vaccination this season
# need to check fluvaxxdate_1 through fluvaxxdate_29
# if any of these dates are between first and last dates of screening for that site
#screen_dates$site <- ifelse(screen_dates$site_long == "CHCO", "M2",
#                            ifelse(screen_dates$site_long == "Lurie", "M3", "M1"))
#eligible_screened_no_contra <- full_join(eligible_screened_no_contra, screen_dates, by = c("site", "season"))
eligible_screened_no_contra <- check_vaccination_dates_new(eligible_screened_no_contra)
eligible_screened_no_contra$vaccine_this_season <- ifelse(eligible_screened_no_contra$priorvacc_summary == 1, 1, 
                                                          eligible_screened_no_contra$vaccine_this_season)
eligible_screened_no_contra_no_vacc <- eligible_screened_no_contra %>% filter(vaccine_this_season == 0)
t4 <- as.data.frame(table(eligible_screened_no_contra_no_vacc$site_long, eligible_screened_no_contra_no_vacc$season))
colnames(t4) <- c("site_long", "season", "Eligible for vaccination")

# patients who received vaccination in the hospital
eligible_screened_no_contra_no_vacc_inhospvacc <- eligible_screened_no_contra_no_vacc %>% filter(vaccine_during_hosp == 1)
t5 <- as.data.frame(table(eligible_screened_no_contra_no_vacc_inhospvacc$site_long, eligible_screened_no_contra_no_vacc_inhospvacc$season))
colnames(t5) <- c("site_long", "season", "Received vaccination in hospital")
t5 <- full_join(t5, t4, by = c("site_long", "season"))
t5$percent_vacc <- round((t5$`Received vaccination in hospital` / t5$`Eligible for vaccination`) * 100,2)
t5 <- t5 %>% arrange(site_long, season)

```

# Methods

- For purposes of finding the first and last date of screening by site and season, the range of possible screening dates was set as August 1 - June 1

# Questions

# Results

## Eligibility criteria

```{r,echo=FALSE}
# Create descriptive table using alldata of eligibility criteria
t1 <- tableby(site ~ eligible_age + eligible_season + eligible_unit + eligible_service, 
              data = data, control = list(digits = 2))
```

```{r, results = "asis"}
summary(t1)
```

## Descriptive statistics after ineligible participants removed

There were `r length(unique(eligible_ptct$pid))` unique eligible patients.

```{r,echo=FALSE}
# Create descriptive table using alldata of eligibility criteria
t_desc <- tableby(site ~ kwt(age_discharge_mo, 'median', 'q1q3') + kwt(age_discharge_yrs, 'median', 'q1q3') +
                  kwt(age_admission_mo, 'median', 'q1q3') + kwt(age_admission_yrs, 'median', 'q1q3') + season +
                    as.factor(unit) + as.factor(race) + as.factor(ethnicity) + as.factor(sex) + as.factor(language) + as.factor(eng_span_other) + 
                    as.factor(insurance) + as.factor(pmca) + as.factor(month_adm), 
              data = eligible, control = list(digits = 2))
```

```{r, results = "asis"}
summary(t_desc)
```

## Screening dates by site and season

```{r, echo=FALSE, comment = ""}
kable(screen_dates)
```

## Count of unique eligible patients by site and season

```{r,echo=FALSE, comment=""}
#kable(eligible_summary)
table(eligible_unique$site_long, eligible_unique$season)
```

# Hospitalizations and screenings

```{r,echo=FALSE, comment=""}
kable(t2)
```

# Contraindications

```{r,echo=FALSE, comment=""}
kable(t3)
```

# Patients screened and eligible for flu vaccine (no contraindication, no vaccination this season)

```{r,echo=FALSE, comment=""}
kable(t4)
```

# Patients screened and eligible and received flu vaccine while in hospital

```{r,echo=FALSE, comment=""}
kable(t5)
```


# Breakpoint model for proportion with contraindications

## Unadjusted

### All sites combined

```{r,echo=FALSE, comment=""}
l <- glm(data = eligible_screened_save, as.factor(contraindication_summary_bin) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = eligible_screened_save[!is.na(eligible_screened_save$season_num),]$season_num, Contraindications = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Contraindications)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))

```

### SCH

```{r,echo=FALSE, comment=""}
sch <- eligible_screened_save %>% dplyr::filter(site == "M1")
l <- glm(data = sch, as.factor(contraindication_summary_bin) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = sch[!is.na(sch$season_num),]$season_num, Contraindications = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Contraindications)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))

```

### CHCO

Model did not converge.

```{r,echo=FALSE, comment=""}
#chco <- eligible_screened_save %>% dplyr::filter(site == "M2")
#l <- glm(data = chco, as.factor(contraindication_summary_bin) ~ season_num, family = "binomial")
#my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
#summary(my.seg)
#slope(my.seg)

# get the fitted data
#my.fitted <- fitted(my.seg)
#my.model <- data.frame(Season = chco[!is.na(sch$season_num),]$season_num, Contraindications = my.fitted)

# plot the fitted model
#ggplot(my.model, aes(x = Season, y = Contraindications)) + geom_line() +
#  scale_x_continuous(breaks = 1:6, 
#                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))
```

### Lurie

```{r,echo=FALSE, comment=""}
lurie <- eligible_screened_save %>% dplyr::filter(site == "M3")
l <- glm(data = lurie, as.factor(contraindication_summary_bin) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = lurie[!is.na(lurie$season_num),]$season_num, Contraindications = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Contraindications)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))
```


## Adjusted for age, site, season, unit, month of year, LOS, race/ethnicity, language and insurance class

### All sites combined

```{r,echo=FALSE, comment=""}
# temp <- eligible_screened_save %>% dplyr::filter(!is.na(season_num) & !is.na(age_discharge_yrs) & !is.na(site) & !is.na(unit) & !is.na(month_adm) &
#                                                    !is.na(los) & !is.na(race) & !is.na(ethnicity) & !is.na(eng_span_other) & !is.na(insurance))
# l <- glm(data = temp, as.factor(contraindication_summary_bin) ~ season_num + age_discharge_yrs + site + unit +
#            + month_adm + los + race + ethnicity + eng_span_other + insurance, family = "binomial")
# my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
# summary(my.seg)
# slope(my.seg)
# 
# # get the fitted data
# my.fitted <- fitted(my.seg)
# my.model <- data.frame(Season = temp$season_num, Contraindications = my.fitted)
# 
# # plot the fitted model
# ggplot(my.model, aes(x = Season, y = Contraindications)) + geom_line() +
#   scale_x_continuous(breaks = 1:6, 
#                     labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))

```

### SCH

```{r,echo=FALSE, comment=""}
# sch <- eligible_screened_save %>% dplyr::filter(site == "M1")
# l <- glm(data = sch, as.factor(contraindication_summary_bin) ~ season_num + age_discharge_yrs + site + unit +
#            + month_adm + los + race + ethnicity + eng_span_other + insurance, family = "binomial")
# my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
# summary(my.seg)
# slope(my.seg)
# 
# # get the fitted data
# my.fitted <- fitted(my.seg)
# my.model <- data.frame(Season = sch[!is.na(sch$season_num),]$season_num, Contraindications = my.fitted)
# 
# # plot the fitted model
# ggplot(my.model, aes(x = Season, y = Contraindications)) + geom_line() +
#   scale_x_continuous(breaks = 1:6, 
#                     labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))

```

### CHCO

Model did not converge.

```{r,echo=FALSE, comment=""}
#chco <- eligible_screened_save %>% dplyr::filter(site == "M2")
#l <- glm(data = chco, as.factor(contraindication_summary_bin) ~ season_num, family = "binomial")
#my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
#summary(my.seg)
#slope(my.seg)

# get the fitted data
#my.fitted <- fitted(my.seg)
#my.model <- data.frame(Season = chco[!is.na(sch$season_num),]$season_num, Contraindications = my.fitted)

# plot the fitted model
#ggplot(my.model, aes(x = Season, y = Contraindications)) + geom_line() +
#  scale_x_continuous(breaks = 1:6, 
#                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))
```

### Lurie

```{r,echo=FALSE, comment=""}
# lurie <- eligible_screened_save %>% dplyr::filter(site == "M3")
# l <- glm(data = lurie, as.factor(contraindication_summary_bin) ~ season_num + age_discharge_yrs + site + unit +
#            + month_adm + los + race + ethnicity + eng_span_other + insurance, family = "binomial")
# my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
# summary(my.seg)
# slope(my.seg)
# 
# # get the fitted data
# my.fitted <- fitted(my.seg)
# my.model <- data.frame(Season = lurie[!is.na(lurie$season_num),]$season_num, Contraindications = my.fitted)
# 
# # plot the fitted model
# ggplot(my.model, aes(x = Season, y = Contraindications)) + geom_line() +
#   scale_x_continuous(breaks = 1:6, 
#                     labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))
```

# Breakpoint model for proportion screened

## All sites combined

```{r,echo=FALSE, comment=""}
l <- glm(data = eligible_screened_save, as.factor(screening) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = eligible_screened_save[!is.na(eligible_screened_save$season_num),]$season_num, Screened = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Screened)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))

```

## SCH

```{r,echo=FALSE, comment=""}
sch <- eligible_screened_save %>% dplyr::filter(site == "M1")
l <- glm(data = sch, as.factor(screening) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = sch[!is.na(sch$season_num),]$season_num, Screened = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Screened)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))

```

## CHCO

```{r,echo=FALSE, comment=""}
chco <- eligible_screened_save %>% dplyr::filter(site == "M2")
l <- glm(data = chco, as.factor(screening) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = chco[!is.na(sch$season_num),]$season_num, Screened = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Screened)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))
```

## Lurie

```{r,echo=FALSE, comment=""}
lurie <- eligible_screened_save %>% dplyr::filter(site == "M3")
l <- glm(data = lurie, as.factor(screening) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = lurie[!is.na(lurie$season_num),]$season_num, Screened = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Screened)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))
```


# Breakpoint model for proportion eligible

## All sites combined

```{r,echo=FALSE, comment=""}
l <- glm(data = data_all, as.factor(eligible) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = data_all[!is.na(data_all$season_num),]$season_num, Eligible = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Eligible)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))

```

## SCH

```{r,echo=FALSE, comment=""}
sch <- data_all %>% dplyr::filter(site == "M1")
l <- glm(data = sch, as.factor(eligible) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = sch[!is.na(sch$season_num),]$season_num, Eligible = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Eligible)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))

```

## CHCO

```{r,echo=FALSE, comment=""}
chco <- data_all %>% dplyr::filter(site == "M2")
l <- glm(data = chco, as.factor(eligible) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = chco[!is.na(sch$season_num),]$season_num, Eligible = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Eligible)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))
```

## Lurie

```{r,echo=FALSE, comment=""}
lurie <- data_all %>% dplyr::filter(site == "M3")
l <- glm(data = lurie, as.factor(eligible) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = lurie[!is.na(lurie$season_num),]$season_num, Eligible = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Eligible)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))
```

# Breakpoint model for proportion receiving vaccination in hospital

## All sites combined

```{r,echo=FALSE, comment=""}
l <- glm(data = eligible_screened_no_contra, as.factor(vaccine_during_hosp) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = eligible_screened_no_contra[!is.na(eligible_screened_no_contra$season_num),]$season_num, Vaccinated = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Vaccinated)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))

```

## SCH

```{r,echo=FALSE, comment=""}
sch <- eligible_screened_no_contra %>% dplyr::filter(site == "M1")
l <- glm(data = sch, as.factor(vaccine_during_hosp) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = sch[!is.na(sch$season_num),]$season_num, Vaccinated = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Vaccinated)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))

```

## CHCO

```{r,echo=FALSE, comment=""}
chco <- eligible_screened_no_contra %>% dplyr::filter(site == "M2")
l <- glm(data = chco, as.factor(vaccine_during_hosp) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = chco[!is.na(sch$season_num),]$season_num, Vaccinated = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Vaccinated)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))
```

## Lurie

```{r,echo=FALSE, comment=""}
lurie <- eligible_screened_no_contra %>% dplyr::filter(site == "M3")
l <- glm(data = lurie, as.factor(vaccine_during_hosp) ~ season_num, family = "binomial")
my.seg <- segmented(l, seg.Z = ~ season_num, psi = list(season_num = c(3)))
summary(my.seg)
slope(my.seg)

# get the fitted data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Season = lurie[!is.na(lurie$season_num),]$season_num, Vaccinated = my.fitted)

# plot the fitted model
ggplot(my.model, aes(x = Season, y = Vaccinated)) + geom_line() +
  scale_x_continuous(breaks = 1:6, 
                    labels = c("2018-2019", "2019-2020", "2020-2021", "2021-2022", "2022-2023", "2023-2024"))
```