---
title: "INFLUENTIAL - PAS abstract"
author: "Laura Pyle"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r libraries,echo=FALSE, include=F}
library(knitr)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(arsenal)
library(stringr)
knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE)
```

```{r,echo=FALSE, include=F}
check_vaccination_dates <- function(data) {
  # Create a new column for the result, default to 0
  data$vaccine_this_season <- 0
  
  # Get column names for vaccination dates
  vaxx_cols <- paste0("fluvaxxdate_", 1:29)
  
  # Loop through each row in the dataset
  for (i in 1:nrow(data)) {
    # Get the screening date range for this person
    first_screen <- data$first_screen[i]
    last_screen <- data$last_screen[i]
    adm_date <- data$adm_date[i]
    dish_date <- data$dish_date[i]
    
    # Skip if screening dates are missing
    if (is.na(first_screen) || is.na(last_screen)) {
      next
    }
    
    # Check each vaccination date column
    for (col in vaxx_cols) {
      # Skip if this vaccination date is missing
      if (is.na(data[[col]][i])) {
        next
      }
      
      # Check if the vaccination date falls within the screening period
      vaxx_date <- data[[col]][i]
      if (vaxx_date >= first_screen && vaxx_date <= last_screen && vaxx_date < adm_date) {
        data$vaccine_this_season[i] <- 1 }
      if (vaxx_date >= first_screen && vaxx_date <= last_screen && vaxx_date >= adm_date 
          && vaxx_date <= dish_date) {
        data$vaccine_during_hosp[i] <- 1 }
    }
  }
  
  return(data)
}
```

```{r data,echo=FALSE,warning=FALSE}
# latest dataset should contain EPIC and Cerner data
redcap <- read.csv('/Users/pylell/Library/CloudStorage/OneDrive-SharedLibraries-UW/Rao/ID Week abstract/Data raw/InFLUentialMainSites_DATA_2025-04-20_1846.csv')

# remove records with missing site number
alldata <- redcap %>% filter(!is.na(site))
alldata$site_long <- ifelse(alldata$site == "M1", "SCH",
                            ifelse(alldata$site == "M2", "CHCO", "Lurie"))

# combine contraindication columns
alldata <- alldata %>% mutate(
  contraindication_summary = pmax(alldata$contraindication, alldata$contraindication2, na.rm = T)
)
# combine previous vaccination columns
alldata <- alldata %>% mutate(
  priorvacc_summary = pmax(alldata$screen_priorvacc1, alldata$screen_priorvacc2, na.rm = T)
)

# first thing to do is to limit the hospitalizations to those between first and last screening date per season
alldata$screen_date1 <- ifelse(alldata$screen_date1 %in% c("", " "), NA, alldata$screen_date1)
alldata$screen_date2 <- ifelse(alldata$screen_date2 %in% c("", " "), NA, alldata$screen_date2)
# find first and last screen date by site
s1 <- alldata %>% select(site, screen_date1)
colnames(s1) <- c("site", "Screen Date")
s2 <- alldata %>% select(site, screen_date2)
colnames(s2) <- c("site", "Screen Date")
s <- rbind(s1, s2)
s$`Screen Date` <- as.Date(s$`Screen Date`, format = "%Y-%m-%d")
s <- s %>% filter(!is.na(`Screen Date`))
s_unique <- unique(s)
# write screening dates to file
#write.csv(s_unique, "/Volumes/pylell/Rao/PHM abstract/screen_dates.csv", row.names = FALSE)

# summarize screening data by site
# first create a variable for season using August 1 as earliest date and June 1 as latest
# using screening data not admissions data because we want to know when sites stopped and started screening
site_data <- alldata
site_data <- site_data %>%
  mutate(
    season = case_when(
      screen_date1>"2018-08-01" & screen_date1<"2019-06-01" ~ "2018-2019",
      screen_date1>"2019-08-01" & screen_date1<"2020-06-01" ~ "2019-2020",
      screen_date1>"2020-08-01" & screen_date1<"2021-06-01" ~ "2020-2021",
      screen_date1>"2021-08-01" & screen_date1<"2022-06-01" ~ "2021-2022",
      screen_date1>"2022-08-01" & screen_date1<"2023-06-01" ~ "2022-2023",
      screen_date1>"2023-08-01" & screen_date1<"2024-06-01" ~ "2023-2024",
      .default = NA
    )
  )
# for purposes of finding earliest and latest screen dates by site and season,
# remove hospitalizations with no screening or outside possible date range
site_data <- site_data %>% filter(!is.na(season))
screen_dates <- site_data %>% group_by(site_long, season) %>% summarise(first_screen = min(screen_date1),
                                                                   last_screen = max(screen_date1))

# in the patient level data, create a variable for season based on admission date
# merge in the site level data by site and season and exclude hospitalizations
# outside the date range for that season
# make sure both admission and discharge are within the first and last dates of screening
alldata <- alldata %>%
  mutate(
    season = case_when(
      adm_date>"2018-08-01" & adm_date<"2019-06-01" ~ "2018-2019",
      adm_date>"2019-08-01" & adm_date<"2020-06-01" ~ "2019-2020",
      adm_date>"2020-08-01" & adm_date<"2021-06-01" ~ "2020-2021",
      adm_date>"2021-08-01" & adm_date<"2022-06-01" ~ "2021-2022",
      adm_date>"2022-08-01" & adm_date<"2023-06-01" ~ "2022-2023",
      adm_date>"2023-08-01" & adm_date<"2024-06-01" ~ "2023-2024",
      .default = NA
    )
  )
alldata <- left_join(alldata, screen_dates, by = c("site_long", "season"))
alldata$in_window <- ifelse(as.Date(alldata$adm_date)>=alldata$first_screen &
                                   as.Date(alldata$dish_date)<=alldata$last_screen, "Y", "N")
# no screening data for Lurie in 2018-2019, so will exclude all admissions there for the season
x <- alldata[is.na(alldata$in_window) | alldata$in_window == "N",]
num_excluded <- nrow(x)

######################
# INCLUSION CRITERIA #
######################

# between 6 months and 18 years at time of discharge
alldata$dish_date <- as.Date(alldata$dish_date)
alldata$adm_date <- as.Date(alldata$adm_date)
alldata$los <- as.numeric(alldata$dish_date - alldata$adm_date)
# all records above seem to have Discharge after Admission 
# no negative LOS, but some 0 LOS
alldata$age_discharge_days <- alldata$age_admission + alldata$los
alldata$age_discharge_yrs <- (alldata$age_admission + alldata$los)/365.25
alldata$age_discharge_mo <- (alldata$age_admission + alldata$los)/30.437

######################
# EXCLUSION CRITERIA #
######################

# apply eligibility criteria
data <- alldata
data$eligible_age <- as.factor(ifelse(data$age_discharge_mo >= 6 & data$age_discharge_yrs <= 18, 1, 0))
# Patient hospitalized on a medical, surgical, rehabilitation, or psychiatry/behavioral medicine unit during the influenza vaccination season at your institution
data$eligible_season <- as.factor(ifelse(!is.na(alldata$in_window) & alldata$in_window == "Y", 1, 0))
data$eligible_unit <- as.factor(ifelse(data$unit == 99, 0, 1))
# Admitted to hematology/oncology service or unit
data$eligible_service <- as.factor(ifelse(is.na(data$service) | data$service == 32, 0, 1))
# Discharged from ICU setting
data$eligible_icu <- as.factor(ifelse(data$icu == 1, 0, 1))
# Ward of state or foster child
# NO CORRESPONDING VARIABLE
# Death on record
# NO CORRESPONDING VARIABLE
# Flagged as “Does not wish to participate in research” 
# NO CORRESPONDING VARIABLE

# remove ineligible patients
eligible <- data %>% filter(eligible_age == 1)
eligible <- eligible %>% filter(eligible_season == 1)
eligible <- eligible %>% filter(eligible_unit == 1)
eligible <- eligible %>% filter(eligible_service == 1)
eligible <- eligible %>% filter(eligible_icu == 1)

# count of unique eligible patients by site and season
eligible_unique <- eligible %>% select(site_long, season, sid) %>% unique()
#eligible_summary <- eligible %>% group_by(site_long, season) %>% summarise(patient_count = tally())

# count of unique hospitalizations for eligible patients by site and season
eligible_hosp_unique <- eligible %>% select(site_long, season, hid) 
#eligible_hosp_summary <- eligible_hosp_unique %>% group_by(site_long, season) %>% summarise(hospitalization_count = tally())

# find hospitalizations who were screened
eligible_screened <- eligible 
eligible_screened <- eligible_screened %>% filter(screening == 1)
es <- as.data.frame(table(eligible_screened$site_long, eligible_screened$season))
colnames(es) <- c("site_long", "season", "# Screenings")

# create a table with number of hospitalizations and screenings
t2 <- as.data.frame(table(eligible_hosp_unique$site_long, eligible_hosp_unique$season))
colnames(t2) <- c("site_long", "season", "hospitalizations")
t2 <- left_join(t2, es, by = c("site_long", "season"))
t2$percent_screened <- round((t2$`# Screenings` / t2$hospitalizations) * 100,2)

# find those screened with contraindications
eligible_screened_contra <- eligible_screened %>% filter(contraindication_summary == 1)
cs <- as.data.frame(table(eligible_screened_contra$site_long, eligible_screened_contra$season))
colnames(cs) <- c("site_long", "season", "# w/ contraindications")
t3 <- as.data.frame(table(eligible_hosp_unique$site_long, eligible_hosp_unique$season))
colnames(t3) <- c("site_long", "season", "hospitalizations")
t3 <- left_join(t3, cs, by = c("site_long", "season"))
t3$`# w/ contraindications` <- ifelse(is.na(t3$`# w/ contraindications`), 0, t3$`# w/ contraindications`)
t3$percent_contraindication <- round((t3$`# w/ contraindications` / t3$hospitalizations) * 100,2)

# Find hospitalizations without contraindications and no vaccination this season (i.e., eligible for vaccine)
eligible_screened_no_contra <- eligible_screened %>% 
  filter(contraindication_summary == 0 | is.na(contraindication_summary))
# determine whether patient had a vaccination this season
# need to check fluvaxxdate_1 through fluvaxxdate_29
# if any of these dates are between first and last dates of screening for that site
#screen_dates$site <- ifelse(screen_dates$site_long == "CHCO", "M2",
#                            ifelse(screen_dates$site_long == "Lurie", "M3", "M1"))
#eligible_screened_no_contra <- full_join(eligible_screened_no_contra, screen_dates, by = c("site", "season"))
eligible_screened_no_contra <- check_vaccination_dates(eligible_screened_no_contra)
eligible_screened_no_contra_no_vacc <- eligible_screened_no_contra %>% filter(vaccine_this_season == 0)
t4 <- as.data.frame(table(eligible_screened_no_contra_no_vacc$site_long, eligible_screened_no_contra_no_vacc$season))
colnames(t4) <- c("site_long", "season", "Eligible for vaccination")
# something not working - some patients both received this season prior to hosp and during hosp

# patients who received vaccination

```

# Methods

- For purposes of finding the first and last date of screening by site and season, the range of possible screening dates was set as August 1 - June 1
- `r num_excluded` hospitalizations with admission date before the first date of screening for the season or with discharge dates after the last date of screening for the season were excluded from analysis
- 11,472 of 78,832 patients had more than one hospitalization. The unit of analysis was hospitalization.

# Questions

1) Since we don't have DOB, it is OK to estimate whether patients are at least 6 months of age using age of 6 * 30 = 180 days?
2) The exclusion criterion states that patients must not be discharged from the ICU. Is it possible someone could be in the ICU at the start of the admission but not discharged from there? If we exclude all records with ICU = 1, ~19k hospitalizations will be excluded
3) Just to confirm: no corresponding variable to check ward of state, foster child, death on record, or flagged as does not wish to participate in research
4) There are a lot of missing values for contraindication. If these were left blank, I assumed there was no contraindication.

# Results

## Eligibility criteria

```{r,echo=FALSE}
# Create descriptive table using alldata of eligibility criteria
t1 <- tableby(site ~ eligible_age + eligible_season + eligible_unit + eligible_service + eligible_icu, 
              data = data, control = list(digits = 2))
```

```{r, results = "asis"}
summary(t1)
```

## Screening dates by site and season

```{r, echo=FALSE, comment = ""}
kable(screen_dates)
```

## Count of unique eligible patients by site and season

```{r,echo=FALSE, comment=""}
#kable(eligible_summary)
table(eligible_unique$site_long, eligible_unique$season)
```

# Hospitalizations and screenings

```{r,echo=FALSE, comment=""}
kable(t2)
```

# Contraindications

```{r,echo=FALSE, comment=""}
kable(t3)
```

# Patients screened and eligible for flu vaccine (no contraindication, no vaccination this season)

```{r,echo=FALSE, comment=""}
kable(t4)
```
