---
title: "INFLUENTIAL - PAS abstract"
author: "Laura Pyle"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r libraries,echo=FALSE, include=F}
library(knitr)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(arsenal)
library(stringr)
knitr::opts_chunk$set(echo = FALSE,warning = FALSE)
```

```{r data,echo=FALSE}
alldata <- read.csv("/Volumes/pylell/Rao/PAS 2025 abstract/InFLUentialEHRData_DATA_LABELS_2024-10-25_1859.csv")
# remove records with missing site number
alldata <- alldata %>% filter(!is.na(Site))

# first thing to do is to limit the hospitalizations to those between first and last screening date per season
alldata$Screen.Date.1 <- ifelse(alldata$Screen.Date.1 %in% c("", " "), NA, alldata$Screen.Date.1)
alldata$Screen.Date.2 <- ifelse(alldata$Screen.Date.2 %in% c("", " "), NA, alldata$Screen.Date.2)
# find first and last screen date by site
s1 <- alldata %>% select(Site, Screen.Date.1)
colnames(s1) <- c("Site", "Screen Date")
s2 <- alldata %>% select(Site, Screen.Date.2)
colnames(s2) <- c("Site", "Screen Date")
s <- rbind(s1, s2)
s$`Screen Date` <- as.Date(s$`Screen Date`, format = "%m/%d/%y")
s <- s %>% filter(!is.na(`Screen Date`))
s_unique <- unique(s)
s_chco <- s_unique %>% filter(Site == "Children's Hospital Colorado")
s_lurie <- s_unique %>% filter(Site == "Lurie Children's Hospital of Chicago")
s_seattle <- s_unique %>% filter(Site == "Seattle Children's Hospital")
s_chco <- s_chco[order(s_chco$`Screen Date`),]
s_lurie <- s_lurie[order(s_lurie$`Screen Date`),]
s_seattle <- s_seattle[order(s_seattle$`Screen Date`),]

# CHCO
# 2023-09-15 - 2024-04-25
# Lurie
# 2019-09-03 - 2020-05-31
# 2020-09-01 - 2021-04-26
# 2021-09-08 - 2022-06-01
# 2022-09-01 - 2023-05-01
# 2023-09-11 - 2024-04-29
# Seattle
# 2023-11-29 - 2024-10-08





# Seattle

site_data <- NULL
site_data$first_screen <- alldata %>% group_by(Site) %>% summarise(min(Screen.Date.1,
                                                                         Screen.Date.2, na.rm = T))
site_data <- as.data.frame(site_data)
colnames(site_data) <- c("Site", "First screen")
last_screen <- NULL
last_screen <- alldata %>% group_by(Site) %>% summarise(max(Screen.Date.1,
                                                                         Screen.Date.2, na.rm = T))
last_screen <- as.data.frame(last_screen)
colnames(last_screen) <- c("Site", "Last screen")
site_data <- left_join(site_data, last_screen, by = "Site")
# need to merge first and last screen date back to patient data
alldata <- left_join(alldata, site_data, by = "Site")
# calculate variable to indicate before first screen or after last screen
alldata$outside_date_range <- ifelse(alldata$Admission.Date.Time)
# include record counts in the table below or just exclude?


######################
# INCLUSION CRITERIA #
######################

# between 6 months and 18 years at time of discharge
alldata$Discharge.Date.Time <- as.Date(alldata$Discharge.Date.Time, format = "%m/%d/%y")
alldata$Admission.Date.Time <- as.Date(alldata$Admission.Date.Time, format = "%m/%d/%y")
alldata$los <- alldata$Discharge.Date.Time - alldata$Admission.Date.Time
# all records above seem to have Discharge after Admission 
# no negative LOS, but some 0 LOS
alldata$age_discharge <- alldata$Age.at.admission.in.days + alldata$los

# apply eligibility criteria
data <- alldata
data <- data %>% filter(age_discharge >= 180 & age_discharge < 6570)
# Patient hospitalized on a medical, surgical, rehabilitation, or psychiatry/behavioral medicine unit during the influenza vaccination season at your institution
data <- data %>% filter(!(Unit == "Other"))

######################
# EXCLUSION CRITERIA #
######################

# Admitted to hematology/oncology service or unit
data <- data %>% filter(!(Service == "Hematology/Oncology"))
# Discharged from ICU setting
data <- data %>% filter(ICU == "No")
# Ward of state or foster child
# NO CORRESPONDING VARIABLE
# Death on record
# NO CORRESPONDING VARIABLE
# Flagged as “Does not wish to participate in research” 
# NO CORRESPONDING VARIABLE


```

# Questions

1) Since we don't have DOB, it is OK to estimate whether patients are at least 6 months of age using age of 6 * 30 = 180 days?
2) The exclusion criterion states that patients must not be discharged from the ICU. Is it possible someone could be in the ICU at the start of the admission but not discharged from there? If we exclude all records with ICU = 1, ~15k hospitalizations will be excluded
3) Just to confirm: no corresponding variable to check ward of state, foster child, death on record, or flagged as does not wish to participate in research
4) 964 records with missing site number - these were excluded
5) To exclude hospitalizations not between the first and last date of screening in a season, I excluded based on the admission date only. Would it be better to require that the discharge date was before the last screening date?

```{r,echo=FALSE}
# Create descriptive table using alldata of eligiblity criteria
t1 <- tableby(Site ~ age_discharge + Unit + Service + ICU, data = alldata, control = list(digits = 2))
```

# Summary statistics on hospitalization data prior to applying eligibility criteria

```{r, include=TRUE, results='asis'}
summary(t1,pfootnote = T)
```
