---
title: "Cooper/Wang CYC study"
author: "Kristen Miller and Laura Pyle"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
library(knitr)
library(gee)
library(geepack)
library(dplyr)
library(emmeans)
library(gtsummary)

knitr::opts_chunk$set(echo = FALSE,warning = FALSE)

```

```{r, include=FALSE}
data <- read.csv("/Volumes/Shared/Shared Projects/Claire/Active/Cooper, Jennifer (1st project)/Resubmission/longdata_03072023.csv")
data <- data %>% arrange(record_id,time)

# convert time to categorical
data$time <- as.factor(data$time)

# make one variable out of lupus nephritis class
data$lupus_nephritis_class <- NA
data[data$lupus_nephritis_class___5=="Checked",]$lupus_nephritis_class <- "V"
data[data$lupus_nephritis_class___5=="Unchecked",]$lupus_nephritis_class <- "III or IV"
# need to check with Kristen about this variable
# numbers don't seem to match the new tables, also there are people with class V checked and class III or IV?
# or should these be separate variables?

# set reference levels
data$gender <- as.factor(data$gender)
data$gender <- relevel(data$gender, ref="Male")
data$race5 <- as.factor(data$race5)
data$race5 <- relevel(data$race5, ref="White/Caucasian")
data$cyclophosphamide_use_2 <- as.factor(data$cyclophosphamide_use_2)
data$cyclophosphamide_use_2 <- relevel(data$cyclophosphamide_use_2, ref="New Onset Lupus Nephritis (no prior treatment)")
data$diagnosis_hypertension <- as.factor(data$diagnosis_hypertension)
data$diagnosis_hypertension <- relevel(data$diagnosis_hypertension, ref="No")
data$lupus_nephritis_class <- as.factor(data$lupus_nephritis_class)
data$lupus_nephritis_class <- relevel(data$lupus_nephritis_class, ref="III or IV")
data$ACEARB <- as.factor(data$ACEARB)
data$ACEARB <- relevel(data$ACEARB, ref="0")
data$Ritux <- as.factor(data$Ritux)
data$Ritux <- relevel(data$Ritux, ref="0")
data$lupus_nephritis_class___5 <- as.factor(data$lupus_nephritis_class___5)
data$lupus_nephritis_class___5 <- relevel(data$lupus_nephritis_class___5, ref="Unchecked")
data$lupus_nephritis_IIIvsIV <- as.factor(data$lupus_nephritis_IIIvsIV)
data$lupus_nephritis_IIIvsIV <- relevel(data$lupus_nephritis_IIIvsIV, ref="III")
data$dose <- as.factor(data$dose)

data <- data %>% filter(!time==0)
data$time <- droplevels(data$time)
```

# Methods

Univariate modeling: Generalized estimating equations were used to test the significance of each predictor in a model also containing a regimen by time interaction. Convergence was poor for models including the baseline time point, so it was excluded. To interpret the significance of each covariate, look at the p-value in the second row in the ANOVA table which is labeled with the name of the covariate.

# Results

## Univariate modeling

### CRR outcome

#### Dose deviation

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ percent_expected_dose + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Age at first dose of CYC

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ age_cyc1_yrs + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Gender

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ gender + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Race/ethnicity

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ race5 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Baseline eGFR

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ diagnosis_GFR10 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Baseline UPC ratio

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ upc_ratio + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Relapsed/refractory LN vs. new-onset LN

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ cyclophosphamide_use_2 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Baseline hypertension

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ diagnosis_hypertension + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Disease duration - LN to CYC

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ duration_ln_to_cyc1 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Disease duration - SLE to CYC

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ duration_sle_to_cyc1 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Lupus nephritis class V

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ lupus_nephritis_class___5 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Lupus nephritis class III or IV

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ lupus_nephritis_IIIvsIV + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Baseline oral prednisone

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ diagnosis_poprednisone + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Baseline ACE/ARB use

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ diagnosis_ACEARB + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Time-varying oral prednisone dose

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ Prednisone + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Time-varying IV steroid dose

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ IVsteroids + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Time-varying ACE/ARB use

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ ACEARB + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Time-varying rituximab use

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ Ritux + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

### CRR or PRR outcome

#### Dose deviation

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ percent_expected_dose + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Age at first dose of CYC

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ age_cyc1_yrs + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Gender

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ gender + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Race/ethnicity

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ race5 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Baseline eGFR

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ diagnosis_GFR10 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Baseline UPC ratio

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ upc_ratio + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Relapsed/refractory LN vs. new-onset LN

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ cyclophosphamide_use_2 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Baseline hypertension

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ diagnosis_hypertension + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Disease duration - LN to CYC

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ duration_ln_to_cyc1 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Disease duration - SLE to CYC

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ duration_sle_to_cyc1 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Lupus nephritis class V

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ lupus_nephritis_class___5 + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Lupus nephritis class III or IV

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ lupus_nephritis_IIIvsIV + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Baseline oral prednisone

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ diagnosis_poprednisone + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Baseline ACE/ARB use

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ diagnosis_ACEARB + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Time-varying oral prednisone dose

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ Prednisone + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Time-varying IV steroid dose

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ IVsteroids + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Time-varying ACE/ARB use

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ ACEARB + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

#### Time-varying rituximab use

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ Ritux + dose*time, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
joint_tests(mod)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
```

### Multivariate model for CRR

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRR ~ dose*time + percent_expected_dose + age_cyc1_yrs + diagnosis_GFR10 + upc_ratio + 
                 cyclophosphamide_use_2 + duration_sle_to_cyc1 + gender + race5 + 
                 Prednisone + IVsteroids + ACEARB + Ritux, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
#joint_tests(mod,rg.limit = 62000)
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
test.emm <- emmeans(mod, ~ dose*time)
pairs(test.emm, adjust="none")
```

### Multivariate model for CRR_PRR

```{r echo=FALSE, comment="", message=FALSE}
mod <-  geeglm(CRRPRR ~ dose*time + percent_expected_dose + age_cyc1_yrs + diagnosis_GFR10 + upc_ratio + 
                 cyclophosphamide_use_2 + duration_sle_to_cyc1 + gender + race5 + 
                 Prednisone + IVsteroids + ACEARB + Ritux, 
               id=record_id, data=data, family=binomial, scale.fix=TRUE, corstr="ar1")
t <- mod %>% tbl_regression(family="binomial", exponentiate = TRUE) %>% add_global_p() 
gtsummary::modify_table_body(t, dplyr::select, -p.value)
test.emm <- emmeans(mod, ~ dose*time)
pairs(test.emm, adjust="none")
```